Compositional Certified Resource Bounds

### 2014-07-03 paper/main.tex
started comparison table
figure caption

@@

File &
\multicolumn{2}{|c|}{KoAT} &
\multicolumn{2}{|c|}{Rank} &
\multicolumn{2}{|c|}{Loopus} &
Speed &
Amortized Automation
\\
\hline

>>>>

\begin{figure*}
\centering
\begin{tabular}{r|c|c|c|c|c}
& KoAT & Rank & LOOPUS & SPEED & AAA \\
\hline
\#bounds &
\\
\#lin.\ bounds &
\\
\#best bounds &

\end{tabular}
\caption{Comparison of our automatic amortized analysis with other
  automatic tools.  We have not been able to obtain a version of
  SPEED~\cite{GulwaniMC09} and just use the bounds that have been
  reported by the authors. Similarly, KoAT~\cite{BrockschmidtEFFG14}
  does currently not work on C programs and we use the bounds that
  have been reported in the author's experimental evaluation.}
\label{fig:compar}
\end{figure*}

@@

File &
\multicolumn{2}{|c|}{KoAT} &
\multicolumn{2}{|c|}{Rank} &
\multicolumn{2}{|c|}{Loopus} &
Speed &
AAA
\\
\hline
